|

### 2019-11-11 analysis/paper/paper.Rmd
Move param-dist figure to supplement (S2)

Second, we compared simulations with ED-2.2 default parameters against simulations using median parameter estimates from a trait meta-analysis (Figure \@ref(fig:param-dist)).
Here, we looked predictions of annual mean C fluxes (gross and net primary productivity, and autotrophic and heterotrophic respiration; Figure \@ref(fig:default-median-flux)) and of summer LAI by PFT (Figure \@ref(fig:default-median-lai)).

@@

```{r param-dist, fig.cap = param_dist_cap}
### Figure 3
param_dist_cap <- paste(
  htmlfig(),
  "Input parameter distributions from PEcAn trait meta-analysis."
)
fig("param-dist.png")
```

Parameter estimates from the trait meta-analysis were often substantially different from the ED-2.2 defaults (Figure \@ref(fig:param-dist)).
In many cases, median parameter estimates were different entirely because of the choice of prior distributions.
However, in several important cases, parameters well-constrained by data produced values substantially different from the ED2 defaults.
For example, ED-2.2 default values for V~cmax~ were too low for all PFTs, and default values for SLA were too low for all PFTs except Early Hardwoods.

@@

These differences in parameter values resulted in ED-2.2 runs that differed from the default runs in several important ways (Figures \@ref(fig:default-median-flux), \@ref(fig:default-median-lai)).
First, in every model configuration (except finite canopy, two-stream RTM, and static traits), gross primary productivity (GPP) reached a higher peak, and did so earlier under median parameters (Figure \@ref(fig:default-median-flux)).
This was driven primarily by higher V~cmax~ and SLA values for most PFTs (Figure \@ref(fig:param-dist)).
However, this increase in GPP was offset by a large increase in autotrophic respiration (RA; Figure \@ref(fig:default-median-flux)), driven primarily by higher growth and leaf respiration rates across all PFTs (notably, the ED-2.2 default is _zero growth respiration_ for all temperate hardwood PFTs; Figure \@ref(fig:param-dist)).
The resulting net primary productivity (NPP) had similar peak values under default and median parameters, though the temporal patterns were quite different in most model configurations (Figure \@ref(fig:default-median-flux)).

@@

Most ED-2.2 runs under-predicted both NPP and LAI, both in the peak period (1920-1950) and towards the end of the simulation (1975-1999) (Figures \@ref(fig:summary-ts-plot), \@ref(fig:pairs-time)).
However, of our five selected representative runs, the two that most closely matched present day composition at UMBS (early hardwood-dominated; **C** and **D** in Figure \@ref(fig:lai-pft-plot)) also closely matched the observed NPP and LAI (Figure \@ref(fig:pairs-time)).
This is encouraging because it suggests that it is possible to get both aggregate ecosystem C fluxes and PFT composition right.
Moreover, given that many important ED-2.2 parameters were well-constrained in our analysis (\@ref(fig:param-dist)), this is possible without using physically unrealistic parameter values.
We therefore suggest that for model calibration and validation, comparisons against multiple output variables---including variables related to composition---can yield maximum constraint and are not unreasonably strict.

@@

**Importantly, efforts to reduce model uncertainty are most effective when they target parameters that are poorly constrained and to which the model is most sensitive**.
For parameters that are already well constrained by data, the marginal value of additional measurements may be limited.
For example, ED-2.2 is highly sensitive to SLA [@dietze_2014_quantitative; @pandit_2018_optimizing], but thanks to the large number of SLA observations, we were able to estimate it very precisely (Figure \@ref(fig:param-dist)) and, as a result, it was not a significant source of uncertainty in our analysis (Figure \@ref(fig:partial-variance-npp)).
At the same time, some poorly constrained parameters have relatively modest impacts on model outputs---for instance, nonlocal dispersal and background mortality rate in our study (Figure \@ref(fig:param-dist), \@ref(fig:partial-variance-npp))---and therefore, reducing their uncertainties is not an effective way to improve model predictions.
Ultimately, this points to the value of model-data feedbacks [@dietze_2013_improving] in advancing ecological research and setting future research agendas.

>>>>

Second, we compared simulations with ED-2.2 default parameters against simulations using median parameter estimates from a trait meta-analysis (Figure S2).
Here, we looked predictions of annual mean C fluxes (gross and net primary productivity, and autotrophic and heterotrophic respiration; Figure \@ref(fig:default-median-flux)) and of summer LAI by PFT (Figure \@ref(fig:default-median-lai)).

@@

Parameter estimates from the trait meta-analysis were often substantially different from the ED-2.2 defaults (Figure S2).
In many cases, median parameter estimates were different entirely because of the choice of prior distributions.
However, in several important cases, parameters well-constrained by data produced values substantially different from the ED2 defaults.
For example, ED-2.2 default values for V~cmax~ were too low for all PFTs, and default values for SLA were too low for all PFTs except Early Hardwoods.

@@

These differences in parameter values resulted in ED-2.2 runs that differed from the default runs in several important ways (Figures \@ref(fig:default-median-flux), \@ref(fig:default-median-lai)).
First, in every model configuration (except finite canopy, two-stream RTM, and static traits), gross primary productivity (GPP) reached a higher peak, and did so earlier under median parameters (Figure \@ref(fig:default-median-flux)).
This was driven primarily by higher V~cmax~ and SLA values for most PFTs (Figure S2).
However, this increase in GPP was offset by a large increase in autotrophic respiration (RA; Figure \@ref(fig:default-median-flux)), driven primarily by higher growth and leaf respiration rates across all PFTs (notably, the ED-2.2 default is _zero growth respiration_ for all temperate hardwood PFTs; Figure S2).
The resulting net primary productivity (NPP) had similar peak values under default and median parameters, though the temporal patterns were quite different in most model configurations (Figure \@ref(fig:default-median-flux)).

@@

Most ED-2.2 runs under-predicted both NPP and LAI, both in the peak period (1920-1950) and towards the end of the simulation (1975-1999) (Figures \@ref(fig:summary-ts-plot), \@ref(fig:pairs-time)).
However, of our five selected representative runs, the two that most closely matched present day composition at UMBS (early hardwood-dominated; **C** and **D** in Figure \@ref(fig:lai-pft-plot)) also closely matched the observed NPP and LAI (Figure \@ref(fig:pairs-time)).
This is encouraging because it suggests that it is possible to get both aggregate ecosystem C fluxes and PFT composition right.
Moreover, given that many important ED-2.2 parameters were well-constrained in our analysis (Figure S2), this is possible without using physically unrealistic parameter values.
We therefore suggest that for model calibration and validation, comparisons against multiple output variables---including variables related to composition---can yield maximum constraint and are not unreasonably strict.

@@

**Importantly, efforts to reduce model uncertainty are most effective when they target parameters that are poorly constrained and to which the model is most sensitive**.
For parameters that are already well constrained by data, the marginal value of additional measurements may be limited.
For example, ED-2.2 is highly sensitive to SLA [@dietze_2014_quantitative; @pandit_2018_optimizing], but thanks to the large number of SLA observations, we were able to estimate it very precisely (Figure S2) and, as a result, it was not a significant source of uncertainty in our analysis (Figure \@ref(fig:partial-variance-npp)).
At the same time, some poorly constrained parameters have relatively modest impacts on model outputs---for instance, nonlocal dispersal and background mortality rate in our study (Figure S2, \@ref(fig:partial-variance-npp))---and therefore, reducing their uncertainties is not an effective way to improve model predictions.
Ultimately, this points to the value of model-data feedbacks [@dietze_2013_improving] in advancing ecological research and setting future research agendas.
